A survey of HTTP caching options on the open Semantic Web

### 2015-01-18 sanity/paper1.tex
Explain rfcs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1001 43ef1190-90fd-4dd7-a769-d0121f02b80e

If used correctly, caching mechanisms will reduce the need to make
HTTP requests, reduce lookups to the backend systems, reduce the need
to make repetitive computations, enable sharing of responses in
Internet infrastructure and reduce latency since requests may be
answered closer to the client.

@@

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client doesn't need to contact the server at
all to reuse a cached response, but this requires a commitment from
the content provider. The standard also gives the client an
opportunity to heuristically determine a time to live. RFC7232, on the
other hand, defines a protocol for asking the server if the cached
response is still fresh using conditional requests. This doesn't
burden the content provider with the task of estimating the time to
live beforehand, but then, it must be able to answer if the resource
has changed less expensively than serving the entire response. These
two approaches can be combined, as a client may ask if a response is
fresh after it has expired. A number of headers are relevant to the
problem, we recorded those in Table~\ref{tab:headers} in
Appendix~\ref{app:fetcher} but they were not all used in this
analysis.\todo{Structured walkthrough}\todo{Impact}

>>>>

If used correctly, caching mechanisms will reduce the need to make
HTTP requests, reduce lookups to the backend systems, reduce the need
to make repetitive computations, enable sharing of responses in
Internet infrastructure, improve uptime and reduce latency since
requests may be answered closer to the client.

@@

As mentioned, two standards are relevant for this study, RFC7234,
which is named ``Caching'' and RFC7232, named ``Conditional
Requests''. The main difference is that the caching standard defines
when a response may be reused without contacting the origin server at
all, whereas the conditional requests define how to validate a
response by contacting the origin server. The two can be combined:
Clients and proxies may use the latter to revalidate a response that
has been cached based on the former.

RFC7234 defines two important headers: \httph{Expires}, whose value is
a date and time of when the response is considered stale, and
therefore should not be used; and \httph{Cache-Control}, which allows
detailed control of the cache, including a \httph{max-age} field,
which gives the time in seconds for how long the the response may be
used from the time of the request. \httph{max-age} takes precedence
over \httph{Expires}. In the following \emph{freshness lifetime} is
understood as the number of seconds that the response may be used
without contacting the origin server. Ideally, the calculation of the
freshness lifetime should be based of the above, but it can also be
based on heuristics, see Section~\ref{sec:simplefresh}.

RFC7232, on the other hand, defines a protocol for asking the server
if the cached response is still fresh using conditional requests. This
doesn't burden the content provider with the task of estimating the
time to live beforehand, but then, it must be able to answer if the
resource has changed less expensively than serving the entire
response. Either of two headers must be set by the server to achieve
this: \httph{ETag}, which sets an opaque identifier for the response,
or \httph{Last-Modified} which gives the time and date of the last
modification of the resource. Clients may use these values to retrieve
the updated response only if the resource has changed. Other relevant
headers are described in Table~\ref{tab:headers}
in Appendix~\ref{app:fetcher} but they were not all used in this
analysis.\todo{Structured walkthrough}\todo{Impact}

In this paper, we study to what extent SPARQL Endpoints, vocabulary
and data publishers support these standards.
